Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-02-09 text/src/article.tex
Spell check

The first line of the scaffold file begins with three dashes. This is
a requirement to indicate the start of a YAML formatted document. Line 2 begins
with a dash character `-' denoting the first entry in the sequence scaffold.
Line 3 is indented by two spaces. Whitespace is used to delimite attributes in
the file. Lines with an incremented level of white space are considered linked
to the first preceeding non-indented line. \pb

@@

The sequence entry in the scaffold file allows multiple sequence-editting
attributes which when applied in different combinations will result in
different output sequence. An example is reverse complementing the sequence
then follwing adding sequence inserts. Performing these actions in the reverse
order will produce a difference output sequence. This section therefore
outlines the scaffolder protocol for processing sequence entries. \pb

@@

\paragraph{Triming sequence:} If the sequence is has start or stop sequences
specified these are used to trip the sequence to these co-ordinates
inclusively. \pb

@@

To ensure that the scaffolder CLI is accessible the RubyGems `bin' directory
should be in the command line path. Assuming that RubyGems are installed in
~/.gem this can be done by adding the following to the ~/.bashrc file. This
should be adjusted for other shells such as zsh etc..

@@

The main aims of scaffolder are two foldfold. The first is produce easy to
install and simplifies the task of genome finishing. The second aim is to
allow to create a tool to facilitate reproducibility in the task of joining
large nucleotide sequences together. \pb

>>>>

The first line of the scaffold file begins with three dashes. This is
a requirement to indicate the start of a YAML formatted document. Line 2 begins
with a dash character `-' denoting the first entry in the sequence scaffold.
Line 3 is indented by two spaces. Whitespace is used to delimit attributes in
the file. Lines with an incremented level of white space are considered linked
to the first preceding non-indented line. \pb

@@

The sequence entry in the scaffold file allows multiple sequence-editing
attributes which when applied in different combinations will result in
different output sequence. An example is reverse complementing the sequence
then following adding sequence inserts. Performing these actions in the reverse
order will produce a difference output sequence. This section therefore
outlines the scaffolder protocol for processing sequence entries. \pb

@@

\paragraph{Trimming sequence:} If the sequence is has start or stop sequences
specified these are used to trip the sequence to these co-ordinates
inclusively. \pb

@@

To ensure that the scaffolder CLI is accessible the RubyGems `bin' directory
should be in the command line path. Assuming that RubyGems are installed in
~/.gem this can be done by adding the following to the ~/.bashrc file. This
should be adjusted for other shells such as Zsh etc..

@@

The main aims of scaffolder are two fold. The first is produce easy to
install and simplifies the task of genome finishing. The second aim is to
allow to create a tool to facilitate reproducibility in the task of joining
large nucleotide sequences together. \pb
